PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added diagnostic chunk for DEP and ANX comorbidity

glad.mhd.raw.id %>%
  freq(depressive_disorders)
```

@@

glad.mhd.raw.id %>%
  freq(anxiety_disorders)
```

@@

@@

glad.mhd.raw.id %>%
  freq(eating_disorders)
```

>>>>

glad.mhd.raw.id %>%
  freq(depressive_disorders,
       cumul = F)
```

@@

glad.mhd.raw.id %>%
  freq(anxiety_disorders,
       cumul = F)
```

@@

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "2" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
```

@@

glad.mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
```
